---
title: "Application of RevelX Theme"
author: "Bob Rietveld, "
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RevelX Theme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Set Up



```{r, fig.show='hold'}

  library(ggplot2)
  library(rxtheme)
  library(trendyy)
  library(tidyverse)
    
# get some google trend data
    q <- c("Bob", "Margot" ,"Marc")
    q_trends <- trendy(q, from = "2019-03-01", to = Sys.Date())
    
```


## Using the defaults

The package is aimed at making it easy to produce RevelX styled content to be used in PowerPoint.

```{r}
# visualize data with all defaults
    q_trends %>% 
    get_interest() %>% 
    ggplot(aes(date, hits, color = keyword)) +
    geom_line() +
    geom_point(alpha = .5) +
    theme_rx() + # apply 
    scale_color_rx()+
    scale_fill_rx()+
    theme(legend.position = "top")
    labs(x = "Time", 
         y = "Relative Search Popularity",
         title = "")
    
```



## Using a different palette

RevelX has a number of predefined palletes. Default "main" uses RevelX theme colors as outlined in the brand guidelines. You can also reverse the color palette by calling ` reverse = TRUE`. 

You can see the available palettes by calling `show_palette`.


```{r}

# show palette
  show_palette()

# create bar chart
    t <-q_trends %>% 
        get_interest() %>% 
        ggplot(aes(date, 
                   hits, 
                   fill = keyword)) +
        geom_bar( stat ="identity") +
        theme_rx( background_color = "transparent" , grid_lines = '#eeeeee' ) + # apply 
        scale_fill_rx( palette = "marc", reverse = T)+
        labs( x = "Time", 
              y = "Relative Search Popularity",
              title = "")
    
    save_rx( plot = t, 
             type = "semi", 
             file_name = "slide_three.png",
             dpi = "print" )

```


## Using discrete vs continous colors

For continous variables you can set a color scheme based on the palette of choice. 

```{r}

# using a different predefined pallete
  ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +  
  theme_rx()+
  scale_fill_rx( palette = "main", 
                 discrete  = F, 
                 reverse = F)


```


## Saving a file

For convenience the save_rx function saves the output in a PowerPoint ready format. the `save_rx` function is a wrapper for `ggsave` and thus supports most features. 

The first argument is the ggplot itself, so it's better to use all the argument names when calling the function. You can pass a ggplot object to the save_rx function so you can automate

  `save_rx( type = "wide", 
            file_name = "slide.png",
            dpi = "screen")`
